copy from oddschecker (open in brave) to thing.txt
run this
pick league in pf.rmd
run that 
predictions should be in a View in the right order for ptf

```{r}
library(tidyverse)
library(conflicted)
source("oddschecker_functions.R")
conflicts_prefer(dplyr::lag)
conflicts_prefer(dplyr::filter)
```




```{r}
filename <- "thing.txt"
lines <- readLines(filename)
lines
```

get (decimal) odds and reformat

```{r}
enframe(lines) %>%
filter(!str_detect(value, "^$")) %>% 
  filter(!str_detect(value, "^[wdl]+$")) %>%
  filter(!str_detect(value, "\\t"))%>% 
  filter(!str_detect(value, "Stats")) %>% 
  filter(!str_detect(value, "logo")) %>% 
  separate(value, into = c("o1", "o2"), convert = TRUE, remove = FALSE, sep = "/") %>% 
  mutate(numberical = as.double(o1) / as.double(o2)) %>% 
  mutate(first = !is.na(lead(numberical, 2)) & is.na(lead(numberical, 1))) %>% 
  mutate(first_team = ifelse(first, value, NA),
         second_team = ifelse(lag(first, 1), value, NA),
         group = cumsum(first)) %>% 
  mutate(item = coalesce(first_team, second_team, as.character(numberical))) %>% 
  drop_na(item) %>% 
  mutate(col_name = case_when(
    !is.na(first_team) ~ "first",
    !is.na(second_team) ~ "second",
    !is.na(numberical) ~ "odds",
    TRUE ~ "error"
  )) %>% 
  select(group, item, col_name) %>% 
pivot_wider(names_from = col_name, values_from = item) %>%
  unnest_legacy(first, second) %>% 
  unnest_wider(odds, names_sep = "_") %>% 
  select(r = group, first, second, starts_with("odds")) -> all_odds
all_odds
```

screenshot page, then upload to google photos, then open in Brave, then select text
might work easier if the thing.txt is just teams and odds

no, use Brave

then convert these to probabilities and find lambdas, as before


```{r}
all_odds %>% 
  mutate(across(starts_with("odds"), ~1/as.numeric(.))) %>% 
  mutate(total = odds_1 + odds_2 + odds_3) %>% 
  mutate(across(starts_with("odds"), ~./total)) %>% 
  select(-total) -> all_odds
all_odds
```

```{r}
all_odds %>% 
  rename(p1 = odds_1, px = odds_2, p2 = odds_3) %>% 
  rowwise() %>% 
  mutate(lambda = list(opt_lambda(c(p1, px, p2)))) %>% 
  unnest_wider(lambda, names_sep = "")  -> dd
dd %>% select(first, second, starts_with("l")) %>% arrange(first)
write_csv(dd, "oc.csv")
```

use this for italian, rounding off