---
title: "Leagues"
output: html_notebook
---


## packages & functions

```{r, message=F}
library(tidyverse)
library(lubridate)
source("20180726_functions.R")
```

## download latest from predictthefootball

```{bash}
./stats.sh | tee stats.txt
```

```{bash}
ls -l stats.txt
```

## how many new predictions?

```{r howmanynew}
stats_old=readRDS("oldstats.rds")
stats_new=read_csv("stats.txt")
saveRDS(stats_new, "oldstats.rds")
stats_new %>% left_join(stats_old, by="game") %>% 
  select(game, league=league.x, new=howmany.x, old=howmany.y) %>% 
  mutate(diff=(new-old)/old*100) %>% 
  group_by(league) %>% 
  summarize(maxdiff=max(diff)) %>% 
  arrange(desc(maxdiff))
stats <- stats_new
```




## retrieve ratings

Estimate new ratings in `ratings` project (first), and check that they are up to date


```{r message=FALSE}
england_post=read_ratings("england", 2020)
england_champ_post=read_ratings("england_champ", 2020)
france_post=read_ratings("france", 2020)
germany_post=read_ratings("germany", 2020)
greece_post=read_ratings("greece", 2020)
italy_post=read_ratings("italy", 2020)
scotland_post=read_ratings("scotland", 2020)
spain_post=read_ratings("spain", 2020)
sweden_post=read_ratings("sweden",2020)
europe_post=read_ratings("europe", 2020)
facup_post=read_ratings("facup", 2020)
```


date of last run (more detail in ratings project)

```{r}
last_posterior_date() %>% 
  separate(fname, into=c("league", "ext"), sep="_post") %>% 
  select(-ext) %>% 
  filter(!str_detect(league,"_pre")) %>% 
  arrange(desc(mtime))
```


## leagues --------------------------

### England

```{r england}
newgames("en",stats)
show_teams(england_post$teams)
is_new=0
txt="
10,17,10,Man City v Burnley,2616,3-0:2-0:3-1:2-1:4-0:1-0:4-1
13,18,10,Leicester v Brighton,2642,2-0:2-1:1-0:1-1:3-1:3-0
9,14,10,Tottenham v West Ham,2750,2-0:2-1:3-1:1-0:1-1:3-0
3,20,10,Man Utd v Sheff Utd,2669,2-0:2-1:1-0:1-1:3-0:3-1
5,6,0,Newcastle v Aston Villa,2659,2-1:1-1:2-0:1-0:1-2:0-1:0-0:3-1
15,8,2,Norwich v Everton,2656,1-2:0-2:0-1:1-1:1-3:1-0:2-1:0-0
12,19,10,Wolves v Bournemouth,2637,2-0:2-1:3-0:1-0:3-1:1-1
4,11,10,Liverpool v Crystal Palace,2639,2-0:2-1:3-0:3-1:1-0:1-1:4-0
17,16,X,Burnley v Watford,2569,1-1:1-0:2-1:1-2:0-1:0-0:2-0:2-2:0-2
7,1,X,Southampton v Arsenal,2592,1-1:2-1:1-2:2-2:1-0:2-0:0-2:0-1:1-3
2,10,2,Chelsea v Man City,2589,1-2:1-1:2-2:1-3:2-1:0-2:2-3
"
d=diff.games(txt,'en',is_new,stats)
d %>% left_join(all_pred(england_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en",stats))
make_new_txt(txt_new, team_tab)
```


### England championship:

```{r england-champ}
newgames("en2",stats)
show_teams(england_champ_post$teams)
is_new=0
txt="
22,7,X,Brentford v West Brom,134,1-1:1-2:2-1:0-2:1-0:2-2
15,6,X,Preston v Cardiff,125,1-1:2-1:1-2:2-0:0-2:1-0
24,9,10,Swansea v Luton,124,2-0:2-1:1-0:1-1:3-0:3-1
17,13,X,Barnsley v Millwall,125,1-1:1-2:2-1:1-0:0-1:0-0:2-0:2-2
18,12,10,Derby v Reading,124,2-1:2-0:1-1:3-1:1-0:1-2:0-0
3,23,10,Birmingham v Hull,124,2-0:2-1:1-0:1-1:1-2:0-1:0-0
2,19,X,Charlton v QPR,124,1-1:2-1:1-2:1-0:0-1:0-0:2-0
8,1,0,Leeds v Fulham,123,2-1:1-1:2-0:1-0:2-2:3-0:3-2:0-0:0-1:3-1
14,4,0,Stoke v Middlesbrough,124,1-1:2-0:2-1:1-0:1-2:0-1:0-2
10,5,X,Wigan v Blackburn,124,1-1:1-2:1-0:2-1:0-1:2-2:0-2
20,21,X,Bristol City v Sheff Wed,123,2-1:1-1:1-2:2-0:1-0:0-1
16,11,10,Nottm Forest v Huddersfield,123,2-0:2-1:1-0:3-0:3-1:1-1:1-2
"
d=diff.games(txt,'en2',is_new,stats)
d %>% left_join(all_pred(england_champ_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en2",stats))
make_new_txt(txt_new, team_tab)
```

### France

```{r france}
newgames("fr",stats)
show_teams(france_post$teams)
is_new=0
txt="
16,20,0,Amiens v Nîmes,15,1-1:2-0:2-1:0-1:1-0
19,17,10,Dijon v Angers,15,1-0:2-1:0-1:1-1:2-0
9,8,0,Lille v Nice,15,1-0:2-0:1-1:2-1:0-1:2-2
2,6,X,Monaco v Bordeaux,14,1-0:2-0:1-1:2-1:0-1:0-2:3-1
15,18,X,Montpellier v Reims,14,1-1:1-0:2-0:0-1:1-2:2-2
3,12,10,PSG v Saint-Étienne,14,2-0:3-1:2-1:4-1:0-1:3-0
7,13,0,Rennes v Metz,14,1-1:2-0:2-1:1-0:0-0:0-1
10,14,1,Strasbourg v Brest,14,2-0:1-0:2-1:0-1:1-1:2-3:3-4
11,4,X,Toulouse v Nantes,14,1-0:1-1:2-0:2-1:2-2:2-3:0-1
1,5,10,Lyon v Marseille,14,2-0:2-1:1-0:0-1:1-1:3-2
"
d=diff.games(txt,'fr',is_new,stats)
d %>% left_join(all_pred(france_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("fr",stats))
make_new_txt(txt_new, team_tab)
```


### Germany

```{r germany}
newgames("de",stats)
show_teams(germany_post$teams)
is_new=0
txt="
2,8,10,Bayern Munich v Freiburg,136,3-0:3-1:2-0:2-1:4-1:4-0
17,15,X,Düsseldorf v Augsburg,135,2-1:1-1:1-2:1-0:0-1:2-0:2-2
11,4,2,Hertha Berlin v B Leverkusen,135,1-2:1-1:0-2:2-1:1-3:2-2:0-1
16,12,10,Hoffenheim v Union Berlin,135,2-1:2-0:1-1:1-0:1-2:3-1:2-2
3,14,X,Köln v Frankfurt,135,1-2:1-1:2-2:0-2:1-0:2-1:1-3:0-1:2-0
13,1,X,Mainz v Werder Bremen,135,2-1:1-2:1-1:1-0:0-1:2-2:0-2:2-0:1-3
10,9,21,Paderborn v B Mgladbach,135,0-2:1-2:1-3:0-3:0-1:0-4:1-4
18,5,X,RB Leipzig v B Dortmund,135,1-1:2-2:2-1:1-2:1-3:2-0:1-0
6,7,X,Schalke v Wolfsburg,135,1-1:2-1:1-2:2-2:0-1:0-0:1-0:0-2:1-3
"

d=diff.games(txt,'de',is_new,stats)
d %>% left_join(all_pred(germany_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("de",stats))
make_new_txt(txt_new, team_tab)
```


### Greece

```{r greece}
newgames("gr",stats)
show_teams(greece_post$teams)
is_new=0
txt="
3,7,10,PAOK Salonika v OFI,106,2-0:3-1:2-1:1-0:3-0:4-0:4-1
4,8,10,AEK Athens v Aris,106,2-0:2-1:1-0:1-1:3-0:3-1
12,11,0,Asteras Tripolis v Atromitos Athens,107,1-1:0-0:2-1:1-2:1-0:0-1:2-0
6,14,0,Xanthi v Panetolikos,106,1-0:1-1:0-0:0-1:2-0:2-1
2,1,0,Olympiakos v Panathinaikos,109,2-1:2-0:1-1:3-0:1-0:3-1:0-0
13,9,0,Larissa v Volos NFC,110,1-0:1-1:2-0:2-1:3-1:0-0:1-2:0-1:2-2
10,5,0,Lamia v Panionios,110,1-1:1-0:2-0:0-0:0-1:2-1:1-2
6,11,X,Xanthi v Atromitos Athens,110,1-1:1-0:0-0:0-1:2-1:1-2:2-0:0-2
"
d=diff.games(txt,'gr',is_new,stats)
d %>% left_join(all_pred(greece_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("gr",stats))
make_new_txt(txt_new, team_tab)
```

### Italy

```{r italy}
newgames("it",stats)
show_teams(italy_post$teams)
is_new=0
txt="
15,4,X,Torino v Parma,162,1-1:1-0:2-1:1-2:2-0:0-1:0-0:0-2:1-3
19,12,X,Hellas Verona v Cagliari,163,1-1:2-1:1-0:0-1:1-2:2-0:3-1:0-0
11,20,10,Atalanta v Sassuolo,158,2-0:2-1:3-0:3-1:1-0
5,8,10,Inter Milan v Sampdoria,160,2-0:2-1:3-1:3-0:1-0
13,9,10,Fiorentina v Brescia,154,2-0:1-0:2-1:3-0:1-1:3-1
14,1,21,Lecce v AC Milan,153,1-2:0-2:0-1:1-1:2-1:1-3
10,3,21,Bologna v Juventus,151,0-2:1-2:1-3:1-1:0-1:0-0
19,16,21,Hellas Verona v Napoli,135,1-2:0-2:0-1:1-3:1-1:2-1:2-2:0-0:1-0
18,12,X,SPAL v Cagliari,159,1-1:1-2:0-1:2-1:0-2:1-0:0-0
17,4,X,Genoa v Parma,157,1-0:2-1:1-1:1-2:2-0:2-2:0-2:0-1
15,7,0,Torino v Udinese,157,2-0:1-1:2-1:1-0:1-2:0-1:3-1
5,20,10,Inter Milan v Sassuolo,139,2-0:3-0:2-1:3-1:1-1:1-0
11,6,X,Atalanta v Lazio,148,2-1:1-1:1-2:2-2:3-2:1-0
2,8,10,Roma v Sampdoria,139,2-0:2-1:3-1:3-0:1-0:1-1
"

d=diff.games(txt,'it',is_new,stats)
d %>% left_join(all_pred(italy_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)

# this needs to be run with d on T
if (is_new) cp_all_pred(italy_post$post,d) %>% select(game,pred) %>% arrange(game)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("it",stats))
make_new_txt(txt_new, team_tab)
```


### Scotland

```{r scotland}
newgames("sc",stats)
show_teams(scotland_post$teams)
is_new=0
txt="
4,9,X,Motherwell v Aberdeen,123,1-2:1-1:2-1:0-2:1-0:2-2:0-1:2-0
5,10,10,Hibernian v St Johnstone,119,2-1:2-0:1-1:1-0:1-2:3-1
7,11,0,Kilmarnock v St Mirren,118,1-1:2-1:1-0:2-0:1-2
8,12,0,Ross County v Hamilton,117,1-1:2-1:1-0:2-0:0-0:1-2:0-1
2,1,X,Rangers v Celtic,115,1-2:2-1:1-1:1-3:1-0:0-2:2-0:2-2:0-1
6,3,X,Livingston v Hearts,115,2-1:1-1:1-0:2-0:1-2:0-1:2-2
"
d=diff.games(txt,'sc',is_new,stats)
d %>% left_join(all_pred(scotland_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("sc",stats))
make_new_txt(txt_new, team_tab)
```


  ### Spain

```{r spain}
newgames("es",stats)
show_teams(spain_post$teams)
is_new=0
txt="
7,6,X,Villarreal v Sevilla,98,1-1:1-2:0-1:2-1:1-0:2-2:0-0
17,20,X,Leganés v Granada,102,1-1:1-0:1-2:2-1:0-1:2-0
13,5,21,Levante v Atl Madrid,119,1-2:0-2:0-1:1-3:1-1:2-1
10,15,X,Real Valladolid v Getafe,119,1-1:1-0:1-2:2-1:0-1:2-0:0-0:0-2
3,4,10,Barcelona v Ath Bilbao,119,3-1:2-0:2-1:3-0:4-1:1-0
14,18,0,Alavés v Osasuna,95,1-1:2-1:1-0:2-0:2-2:1-2
9,12,0,Real Sociedad v Celta Vigo,95,2-0:2-1:1-1:2-2:1-0:1-2
2,19,10,Real Madrid v Mallorca,95,3-0:3-1:2-0:4-0:1-0:2-1:4-1:5-0
16,1,21,Eibar v Valencia,82,1-2:0-1:1-1:0-2
8,11,0,Real Betis v Espanyol,82,1-1:2-1:2-0:1-2:1-0
"
d=diff.games(txt,'es',is_new,stats)
d %>% left_join(all_pred(spain_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("es",stats))
make_new_txt(txt_new, team_tab)
```



### Sweden

```{r sweden}
newgames("se",stats)
show_teams(sweden_post$teams)
is_new=0
txt="
12,3,X,Falkenbergs FF v Kalmar FF,71,1-1:2-1:2-2:1-2:0-1:0-2:1-0
11,5,1,IFK Norrköping v Djurgårdens IF,71,1-2:2-1:2-0:1-0:1-1:2-2:3-1
1,15,10,Malmö FF v Varbergs BoIS,71,3-0:2-0:2-1:1-0:3-1:4-0:5-0
2,6,X,Hammarby IF v AIK,72,1-2:1-1:2-0:1-0:2-2:0-0:2-1
8,16,0,Örebro SK v Östersunds FK,71,2-1:1-1:2-0:2-2:0-0:0-1:3-2:1-3:1-0
7,10,2,Helsingborgs IF v IF Elfsborg,71,0-2:1-2:1-1:0-3:2-1:0-0:1-0:2-0:2-2
4,9,0,IFK Göteborg v Mjällby AIF,71,2-0:2-1:3-0:1-1:1-2:2-2:3-1:4-1:1-0
14,13,1,IK Sirius v BK Häcken,71,0-1:1-0:2-1:1-1:2-0:1-2:2-2
"
d=diff.games(txt,'se',is_new,stats)
d %>% left_join(all_pred(sweden_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```

### champions league

```{r}
newgames("euc",stats)
show_teams(europe_post$teams)
is_new=0
txt="
418,98,2,Atl Madrid v Liverpool,329,1-1:1-2:2-1:0-1:0-2:1-3:1-0
166,138,X,B Dortmund v PSG,329,1-2:2-1:2-2:1-1:1-3:2-3:3-1:0-1:2-0:0-2
240,414,X,Atalanta v Valencia,340,1-1:2-1:1-2:2-0:1-0:2-2:3-1:0-1:0-2
103,653,X,Tottenham v RB Leipzig,339,2-1:1-1:1-2:2-0:3-1:1-0:2-2
96,163,2,Chelsea v Bayern Munich,334,1-2:1-3:1-1:2-2:0-2:2-1:2-3
245,416,2,Napoli v Barcelona,334,1-2:1-1:0-2:1-3:2-1:2-2
136,232,21,Lyon v Juventus,340,1-2:0-2:0-1:1-3:1-1:0-3
415,104,X,Real Madrid v Man City,340,2-1:1-1:2-2:1-2:3-1:2-0
653,103,0,RB Leipzig v Tottenham,315,2-1:1-1:2-0:1-2:3-1
414,240,0,Valencia v Atalanta,314,2-1:2-0:1-2:1-1:1-0:2-2:3-1
98,418,10,Liverpool v Atl Madrid,295,2-0:2-1:3-1:1-0:1-1:3-0
138,166,10,PSG v B Dortmund,294,2-1:2-0:3-1:2-2:1-1:3-2:1-2:1-0
232,136,10,Juventus v Lyon,243,2-0:3-0:3-1:2-1:1-0:1-1
104,415,0,Man City v Real Madrid,243,2-1:2-2:1-1:3-1:1-2:2-0:1-0:3-0:1-3
416,245,10,Barcelona v Napoli,242,2-1:2-0:3-1:3-0:1-1
163,96,10,Bayern Munich v Chelsea,242,2-1:3-1:2-0:3-0:4-1:1-1
"
d=diff.games(txt,'euc',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("euc",stats))
make_new_txt(txt_new, team_tab)
```

### europa league


```{r europa}
newgames("eue",stats)
show_teams(europe_post$teams)
is_new=0
txt="
175,445,10,Frankfurt v FC Basel,111,2-1:2-0:3-1:1-1:1-2:1-0:3-0
513,84,X,Istanbul Basaksehir v FC Copenhagen,111,2-1:1-0:1-1:1-2:2-0:0-1:0-0
20,97,21,LASK v Man Utd,111,1-2:0-2:1-1:0-3:0-1:1-3:2-1:1-0
419,231,0,Sevilla v Roma,109,2-1:1-1:1-0:1-2:2-0:2-2:0-0:3-1
234,428,10,Inter Milan v Getafe,109,2-0:2-1:3-1:3-0:1-1:1-0
180,106,X,Olympiakos v Wolves,110,1-1:1-2:2-1:2-2:0-1:0-0:1-0
381,165,1,Rangers v B Leverkusen,110,1-2:1-1:2-1:0-2:1-0:1-3:2-0
168,467,0,Wolfsburg v Shakhtar Donetsk,110,2-0:2-1:1-1:1-2:2-2:1-0:3-1
165,381,0,B Leverkusen v Rangers,49,2-1:2-0:2-2:1-0:3-1:1-1:1-2:3-0
428,234,2,Getafe v Inter Milan,47,1-1:1-2:0-2:1-3:1-0:2-2:0-1:2-1
467,168,X,Shakhtar Donetsk v Wolfsburg,47,2-1:1-1:1-2:1-0:2-0:0-1:3-1
106,180,10,Wolves v Olympiakos,47,2-1:2-0:1-1:3-0:3-1:3-2:1-0
445,175,X,FC Basel v Frankfurt,47,1-1:2-1:1-2:2-2:1-0:0-1:2-0:3-1
84,513,0,FC Copenhagen v Istanbul Basaksehir,47,2-1:2-0:1-1:1-0:1-2:0-0:3-1
97,20,10,Man Utd v LASK,47,3-1:3-0:2-0:2-1:1-0:4-0:5-0:1-1
231,419,X,Roma v Sevilla,47,2-1:1-1:2-0:1-2:2-2:0-1:1-0:2-3:3-1 
"
d=diff.games(txt,'eue',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("eue",stats))
make_new_txt(txt_new, team_tab)
```

### fa cup

```{r facup}
newgames("enf",stats)
show_teams(facup_post$teams)
is_new=0
txt="
14,1,21,Portsmouth v Arsenal,171,0-2:1-2:1-3:1-1:0-3:2-1:2-2
2,4,1,Chelsea v Liverpool,184,1-2:2-1:1-1:2-0:0-1:0-2:2-2
29,28,21,Reading v Sheff Utd,182,1-2:0-2:0-1:1-1:2-1:1-0:1-3
19,5,X,West Brom v Newcastle,183,2-1:1-1:1-2:2-0:1-0:2-2:0-1
23,10,10,Leicester v Birmingham,186,2-0:2-1:3-0:3-1:1-1:1-0
60,17,21,Sheff Wed v Man City,184,0-3:1-3:0-2:1-2:0-4:1-4
16,18,10,Tottenham v Norwich,185,2-0:2-1:3-0:3-1:1-0
40,3,21,Derby v Man Utd,183,1-2:0-2:1-3:1-1:2-1:2-2:0-1
"
d=diff.games(txt,'enf',is_new,stats)
d %>% left_join(all_pred(facup_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("enf",stats))
make_new_txt(txt_new, team_tab)
```


### junk

league
<chr>
maxdiff
<dbl>
gr	23.529412			
fr	22.500000			
eue	20.388350			
de	18.367347			
sc	16.822430			
en2	16.190476			
es	13.725490			
it	12.244898			
euc	11.147541			
enf	2.061856	


```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```