---
title: "Leagues"
output: html_notebook
---

## packages & functions

```{r, message=F}
library(tidyverse)
library(lubridate)
source("20180726_functions.R")
```

## download latest from predictthefootball

```{bash}
./stats.sh | tee stats.txt
```

## last prediction d/l

```{bash}
ls -l stats.txt
```

## how many new predictions?

```{r howmanynew}
stats_old=readRDS("oldstats.rds")
stats_new=read_csv("stats.txt")
saveRDS(stats_new, "oldstats.rds")
stats_new %>% left_join(stats_old, by="game") %>% 
  select(game, league=league.x, new=howmany.x, old=howmany.y) %>% 
  mutate(diff=(new-old)/old*100) %>% 
  group_by(league) %>% 
  summarize(maxdiff=max(diff)) %>% 
  arrange(desc(maxdiff))
stats <- stats_new
Sys.time()
```

## retrieve ratings

Estimate new ratings in `ratings` project (first), and check that they are up to date

```{r message=FALSE}
england_post=read_ratings("england", 2021)
england_champ_post=read_ratings("england_champ", 2021)
france_post=read_ratings("france", 2021)
germany_post=read_ratings("germany", 2021)
greece_post=read_ratings("greece", 2021)
italy_post=read_ratings("italy", 2021)
scotland_post=read_ratings("scotland", 2021)
spain_post=read_ratings("spain", 2021)
sweden_post=read_ratings("sweden",2020)
europe_post=read_ratings("europe", 2020)
facup_post=read_ratings("facup", 2020)
```

date of last run (more detail in ratings project)

```{r}
last_posterior_date() %>% 
  separate(fname, into=c("league", "ext"), sep="_post") %>% 
  select(-ext) %>% 
  filter(!str_detect(league,"_pre")) %>% 
  arrange(desc(mtime))
```

## leagues --------------------------

### England

```{r england}
newgames("en",stats)
show_teams(england_post$teams)
is_new=0
txt="
8,4,X,Everton v Liverpool,4539,2-2:1-2:2-1:1-1:1-3:2-3:3-2
2,7,10,Chelsea v Southampton,4674,2-0:2-1:3-1:3-0:1-1
10,1,0,Man City v Arsenal,4697,2-1:3-1:2-2:1-2:1-1:2-0:3-2
5,3,X,Newcastle v Man Utd,4708,1-2:1-1:2-1:1-3:0-2:2-2:0-1:1-0
16,11,10,Sheff Utd v Fulham,4683,2-0:1-0:2-1:1-1:0-0:3-1:1-2
12,19,0,Crystal Palace v Brighton,4707,1-1:2-1:1-2:1-0:2-0:2-2:0-1
9,15,10,Tottenham v West Ham,4724,2-1:3-1:2-0:3-0:3-2:2-2:1-1:4-1
14,6,0,Leicester v Aston Villa,4731,2-1:2-2:2-0:1-1:3-1:1-2:1-0:3-2
17,18,X,West Brom v Burnley,4692,1-1:2-1:1-2:0-1:1-0:0-0:2-0:2-2:0-2
20,13,X,Leeds v Wolves,4689,2-1:2-2:1-1:1-2:2-0:3-2:3-1:1-0
"
d=diff.games(txt,'en',is_new,stats)
d %>% left_join(all_pred(england_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en",stats))
make_new_txt(txt_new, team_tab)
```

### England championship:

```{r england-champ}
newgames("en2",stats)
show_teams(england_champ_post$teams)
is_new=0
txt="
17,4,10,Bristol City v Middlesbrough,121,2-1:2-0:1-0:1-1:3-1:3-0:1-2
2,24,2,Coventry v Swansea,120,1-2:1-1:0-1:0-2:1-3:2-1:1-0
23,15,X,Huddersfield v Derby,121,1-1:2-0:2-1:1-0:1-2:0-1:2-2:0-0
10,18,0,Millwall v Luton,122,2-1:2-0:1-1:1-0:3-1
1,3,10,Norwich v Birmingham,122,2-0:2-1:1-0:1-1:3-1:0-2:0-0
14,8,10,Nottm Forest v Rotherham,122,2-0:1-0:2-1:1-1:0-1:3-1:3-0
9,22,10,Reading v Wycombe,120,2-0:3-0:2-1:1-0:1-1:3-1:4-0
12,7,X,Cardiff v Bournemouth,116,1-1:1-2:2-1:0-1:0-2:1-0:2-0:2-2
16,13,X,QPR v Preston,117,2-1:1-1:1-2:1-0:2-2:0-1:0-0:2-0
20,21,X,Sheff Wed v Brentford,116,1-2:1-1:2-1:0-1:1-0:2-2:0-2
11,19,10,Stoke v Barnsley,116,2-0:1-0:2-1:3-0:1-1:3-1:0-1
6,5,0,Watford v Blackburn,116,2-1:2-0:1-1:1-0:2-2:3-0:3-2   
"
d=diff.games(txt,'en2',is_new,stats)
d %>% left_join(all_pred(england_champ_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en2",stats))
make_new_txt(txt_new, team_tab)
```

### France

```{r france}
newgames("fr",stats)
show_teams(france_post$teams)
is_new=0
txt="
19,7,21,Dijon v Rennes,118,1-2:0-2:1-1:0-1:1-0:2-1:1-3:0-0:0-3:2-2
20,3,21,Nîmes v PSG,127,1-3:1-2:0-2:0-4:1-4:0-1:0-3
17,15,10,Reims v Lorient,130,2-1:1-1:2-0:1-0:0-1:1-2:3-1
5,6,10,Marseille v Bordeaux,130,2-1:2-0:1-1:1-0:1-2:0-1:2-2:3-1
11,1,21,Strasbourg v Lyon,130,1-2:1-3:0-2:1-1:0-1:2-2:2-1
16,10,X,Angers v Metz,131,2-1:1-1:2-0:1-0:0-1:1-2:0-0:2-2
2,14,0,Monaco v Montpellier,131,2-1:1-0:2-0:1-1:2-2:3-1:1-2:0-1
4,18,10,Nantes v Brest,131,2-1:2-0:1-0:1-1:0-1:2-2:1-2
13,8,0,Saint-Étienne v Nice,131,2-1:1-1:1-0:2-2:0-1:0-2:1-2:2-0
9,12,0,Lille v Lens,131,2-1:2-0:1-1:1-0:2-2:3-1:1-2:0-1
"
d=diff.games(txt,'fr',is_new,stats)
d %>% left_join(all_pred(france_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("fr",stats))
make_new_txt(txt_new, team_tab)
```

### Germany

```{r germany}
newgames("de",stats)
show_teams(germany_post$teams)
is_new=0
txt="
13,18,21,Augsburg v RB Leipzig,155,1-2:1-3:0-2:1-1:0-3:2-2:0-0
7,1,X,Freiburg v Werder Bremen,155,1-1:1-2:2-1:2-2:0-1:1-0:0-0:0-2
9,15,10,Hertha Berlin v Stuttgart,155,2-1:1-0:2-0:1-1:3-1:1-2:2-2
14,4,21,Hoffenheim v B Dortmund,155,1-2:1-3:2-2:0-2:1-1:2-1:0-3:2-3:0-1
10,3,2,Mainz v B Leverkusen,155,1-2:0-2:1-1:0-1:1-3:1-0:2-1:0-3
17,2,21,Arminia Bielefeld v Bayern Munich,155,0-2:0-4:0-3:1-3:0-5:1-2:1-4:0-1
8,6,10,B Mgladbach v Wolfsburg,156,2-1:1-0:1-1:2-0:3-1:0-0:2-2:3-0:3-2
12,11,2,Köln v Frankfurt,157,1-2:1-1:0-2:1-3:2-1:0-1:1-0
5,16,X,Schalke v Union Berlin,157,2-1:1-1:1-0:0-2:1-2:2-0:3-1:0-1:3-0
"

d=diff.games(txt,'de',is_new,stats)
d %>% left_join(all_pred(germany_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("de",stats))
make_new_txt(txt_new, team_tab)
```

### Greece

```{r greece}
newgames("gr",stats)
show_teams(greece_post$teams)
is_new=0
txt="
14,6,X,Volos NFC v PAS Giannina,115,1-1:2-1:1-0:0-0:2-0:1-2:0-2:0-1:2-2
8,5,10,Aris v Apollon Smyrnis,119,2-0:2-1:1-0:3-0:1-1:3-1
2,9,10,Olympiakos v Atromitos Athens,123,2-0:2-1:1-0:3-0:3-1:1-1
7,1,X,OFI v Panathinaikos,130,1-1:1-2:0-1:1-0:2-0:2-1:0-2
10,13,X,Larissa v Asteras Tripolis,130,1-1:1-0:1-2:0-0:0-1:2-0:2-1:0-2
4,3,0,AEK Athens v PAOK Salonika,131,2-1:1-1:1-0:1-2:2-0:2-2:0-0:0-1:0-2
12,11,0,Lamia v Panetolikos,129,1-0:1-1:0-0:2-0:2-1:0-1:1-2
"
d=diff.games(txt,'gr',is_new,stats)
d %>% left_join(all_pred(greece_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("gr",stats))
make_new_txt(txt_new, team_tab)
```

### Italy

```{r italy}
newgames("it",stats)
show_teams(italy_post$teams)
is_new=01
txt="
20,15,X,Sassuolo v Torino,22,2-1:1-1:0-0:0-2:1-0:1-2:2-0:2-2:2-3:3-0:3-1
12,8,10,Atalanta v Sampdoria,22,2-0:2-1:1-1:3-0:0-0:1-0:1-2:2-3:3-1:3-2
17,5,2,Genoa v Inter Milan,22,0-2:1-2:1-1:1-3:0-0:0-1:1-4:2-1:2-3:3-0
6,9,10,Lazio v Bologna,22,2-0:3-0:1-0:2-1:1-1:4-1:0-0:0-2:1-2:3-2
13,10,X,Cagliari v Crotone,22,1-0:1-2:2-0:1-1:2-1:0-0:0-1:3-0:3-1:3-2
19,16,21,Benevento v Napoli,22,1-2:0-2:1-3:0-1:0-3:2-1:2-3:0-0:1-1:1-4:3-0
4,11,0,Parma v SPEZ,22,1-0:1-1:1-2:2-0:2-1:3-0:0-0:2-2:3-1:3-2
14,7,10,Fiorentina v Udinese,22,2-1:1-0:2-0:1-1:1-2:3-2:0-0:1-3:3-0:3-1
3,18,10,Juventus v Hellas Verona,21,2-0:3-0:1-2:2-1:3-1:1-0:3-2:4-0:5-1
1,2,0,AC Milan v Roma,23,2-1:1-1:2-0:0-0:1-0:3-2:0-1:1-2:2-2:3-0:3-1:4-2
"

d=diff.games(txt,'it',is_new,stats)
d %>% left_join(all_pred(italy_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)

# this needs to be run with d on T
if (is_new) cp_all_pred(italy_post$post,d) %>% select(game,pred) %>% arrange(game)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("it",stats))
make_new_txt(txt_new, team_tab)
```

idea: get predictions from new and old stats, and display only the different ones

### Scotland

```{r scotland}
newgames("sc",stats)
show_teams(scotland_post$teams)
is_new=0
txt="
1,2,0,Celtic v Rangers,302,2-1:1-1:1-2:3-1:2-2:2-0
3,8,2,Dundee Utd v Aberdeen,304,1-2:1-1:0-1:0-2:1-3:2-2:2-1
12,9,X,Hamilton v St Johnstone,304,1-1:1-0:2-1:1-2:0-1:0-0:0-2:2-2
6,7,X,Livingston v Kilmarnock,304,1-1:2-1:1-2:1-0:2-0:0-1:0-2
10,5,21,Ross County v Hibernian,303,1-2:0-2:1-3:1-1:0-1:0-3
8,12,10,Aberdeen v Hamilton,279,2-0:2-1:1-0:3-0:1-1:3-1
"
d=diff.games(txt,'sc',is_new,stats)
d %>% left_join(all_pred(scotland_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("sc",stats))
make_new_txt(txt_new, team_tab)
```

### Spain

```{r spain}
newgames("es",stats)
show_teams(spain_post$teams)
is_new=0
txt="
20,6,2,Granada v Sevilla,161,1-2:1-1:0-2:1-3:0-1:0-0:2-2
14,5,21,Celta Vigo v Atl Madrid,165,1-2:0-2:1-3:0-1:1-1
2,10,10,Real Madrid v Cádiz,162,3-0:2-0:4-0:3-1:1-0:2-1:5-0
17,3,21,Getafe v Barcelona,165,0-2:1-2:1-3:0-3:0-1:1-1:2-2
18,7,X,Eibar v Osasuna,163,1-1:2-1:2-0:0-1:1-0:1-2:0-0:0-2:2-2
4,15,10,Ath Bilbao v Levante,163,2-1:1-0:2-0:1-1:1-2:3-1:0-1:2-2
8,1,X,Villarreal v Valencia,164,1-1:2-1:2-2:2-0:1-2:1-0:0-1:0-2:1-3
16,13,0,Alavés v Elche,164,2-0:1-0:1-1:2-1:0-0:1-2:0-1
19,12,X,Huesca v Real Valladolid,164,1-0:1-1:1-2:2-1:0-0:0-2:0-1:2-2
9,11,X,Real Betis v Real Sociedad,164,2-1:1-1:2-0:2-2:1-2:0-1:1-0:0-0
"
d=diff.games(txt,'es',is_new,stats)
d %>% left_join(all_pred(spain_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("es",stats))
make_new_txt(txt_new, team_tab)
```

### Sweden

```{r sweden}
newgames("se",stats)
show_teams(sweden_post$teams)
is_new=0
txt="
12,8,X,Falkenbergs FF v Örebro SK,91,1-2:0-2:1-1:2-1:1-0:1-3:0-0:3-0
2,9,10,Hammarby IF v Mjällby AIF,96,2-0:2-1:3-0:1-0:2-2:3-1:1-1:0-0:0-1
10,3,10,IF Elfsborg v Kalmar FF,96,2-1:2-0:1-1:1-0:3-0:3-1:2-2
14,16,X,IK Sirius v Östersunds FK,96,2-1:1-1:2-0:1-0:0-1:0-2:2-2:0-0:1-2
6,4,0,AIK v IFK Göteborg,97,1-0:1-1:2-1:2-0:0-1:3-0:3-1:0-0:1-2
15,11,21,Varbergs BoIS v IFK Norrköping,97,1-2:0-2:0-3:0-1:1-1:1-0:1-3
5,1,X,Djurgårdens IF v Malmö FF,94,1-2:1-1:0-2:2-1:0-1:1-0:0-3:2-0:2-3
7,13,X,Helsingborgs IF v BK Häcken,95,1-2:1-1:0-2:0-1:2-1:0-0:1-0:2-0:1-3:2-2
"
d=diff.games(txt,'se',is_new,stats)
d %>% left_join(all_pred(sweden_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```

or api.clubelo.com/Fixtures (csv)

### champions league

```{r}
newgames("euc",stats)
show_teams(europe_post$teams)
is_new=0
txt="
240,138,1,Atalanta v PSG,191,1-2:1-3:2-1:0-2:2-2:1-1:2-3:3-2
653,418,21,RB Leipzig v Atl Madrid,201,1-2:0-1:1-1:0-2:2-1:1-3:1-0:2-2
416,163,1,Barcelona v Bayern Munich,200,1-2:1-3:2-1:2-2:2-3:1-1:0-2
104,136,10,Man City v Lyon,193,3-1:2-1:2-0:3-0:4-1:1-0
653,138,1,RB Leipzig v PSG,168,1-2:1-3:2-1:1-0:1-1:2-2:0-1:0-2
136,163,21,Lyon v Bayern Munich,181,1-3:1-4:1-2:0-2:0-3:0-4:1-1
138,163,1,PSG v Bayern Munich,166,1-2:1-3:2-1:2-3:2-4:2-0:1-1:2-2
"
d=diff.games(txt,'euc',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("euc",stats))
make_new_txt(txt_new, team_tab)
```

### europa league

```{r europa}
newgames("eue",stats)
show_teams(europe_post$teams)
is_new=0
txt="
234,165,10,Inter Milan v B Leverkusen,93,2-1:2-0:1-1:1-0:3-1:1-2
97,84,10,Man Utd v FC Copenhagen,93,2-0:3-1:2-1:3-0:1-0:1-1
467,445,1,Shakhtar Donetsk v FC Basel,108,2-1:2-0:1-2:1-1:1-0:3-1:0-1
106,419,X,Wolves v Sevilla,108,1-2:2-1:1-1:1-0:0-2:1-3:2-2
419,97,X,Sevilla v Man Utd,73,1-2:2-1:1-1:1-0:1-3:2-0:0-0:0-2
234,467,10,Inter Milan v Shakhtar Donetsk,97,2-1:2-0:3-1:3-0:1-0:1-1:1-2:2-2
419,234,1,Sevilla v Inter Milan,94,1-2:1-3:2-1:0-2:1-0:1-1:2-2
"
d=diff.games(txt,'eue',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("eue",stats))
make_new_txt(txt_new, team_tab)
```

### fa cup

```{r facup}
newgames("enf",stats)
show_teams(facup_post$teams)
is_new=0
txt="
18,3,21,Norwich v Man Utd,150,0-2:1-3:1-2:0-3:0-4:0-1:1-1
28,1,X,Sheff Utd v Arsenal,154,1-2:2-1:1-1:1-0:0-1
23,2,X,Leicester v Chelsea,155,1-2:2-1:1-1:1-3:2-2
5,17,21,Newcastle v Man City,157,0-2:1-3:0-3:1-2:2-1
1,17,21,Arsenal v Man City,148,1-2:1-3:0-2:2-1:0-3
3,2,1,Man Utd v Chelsea,157,2-1:1-2:3-1:1-1:2-0:2-2:3-2
1,2,1,Arsenal v Chelsea,92,1-2:2-1:1-3:1-1:2-3:0-2:2-2:0-1
"
d=diff.games(txt,'enf',is_new,stats)
d %>% left_join(all_pred(facup_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("enf",stats))
make_new_txt(txt_new, team_tab)
```

## clubelo

```{r}
library(tidyverse)
fixtures0 <- read_csv("http://api.clubelo.com/Fixtures")
fixtures0 %>% 
  select(-starts_with("GD")) %>% 
  pivot_longer(starts_with("R:"), names_to = "result", values_to = "prob") %>% 
  extract(result, into = c("s1", "s2"), regex = "R:(.)-(.)", convert = TRUE) %>% 
  nest_by(Date, Country, Home, Away) -> fixtures
fixtures
```
data has columns s1, s2, prob

write function to get best expected point prediction per ptf


add bonuses to this

```{r}
ptf <- function(p1, p2, s1, s2) {
  case_when(
    p1 == s1 & p2 == s2 ~ 3,
    p1 > p2 & s1 > s2   ~ 1,
    p1 == p2 & s1 == s2 ~ 1,
    p1 < p2 & s1 < s2   ~ 1,
    TRUE                ~ 0
  )  
}
```


```{r}
best_pred <- function(p) {
  prd <- crossing(p1=0:6, p2=0:6)
  prd %>% crossing(p) %>% 
    mutate(pts = ptf(p1, p2, s1, s2)) %>% 
    group_by(p1, p2) %>% 
    summarise(ept = sum(pts*prob)) %>% 
    ungroup() %>% 
    filter(ept==max(ept)) -> d
  str_c(d$p1, " - ", d$p2)
}
```



```{r}
fixtures %>% 
  summarize(pred = best_pred(data)) %>% View("clubelo")
```

## run to here

### junk

league <chr> maxdiff <dbl> gr 23.529412\
fr 22.500000\
eue 20.388350\
de 18.367347\
sc 16.822430\
en2 16.190476\
es 13.725490\
it 12.244898\
euc 11.147541\
enf 2.061856

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```
