---
title: "Leagues"
output: html_notebook
---


## packages & functions

```{r, message=F}
library(tidyverse)
library(lubridate)
source("20180726_functions.R")
```

## download latest from predictthefootball

```{bash}
./stats.sh | tee stats.txt
```

## last prediction d/l

```{bash}
ls -l stats.txt
```

## how many new predictions?

```{r howmanynew}
stats_old=readRDS("oldstats.rds")
stats_new=read_csv("stats.txt")
saveRDS(stats_new, "oldstats.rds")
stats_new %>% left_join(stats_old, by="game") %>% 
  select(game, league=league.x, new=howmany.x, old=howmany.y) %>% 
  mutate(diff=(new-old)/old*100) %>% 
  group_by(league) %>% 
  summarize(maxdiff=max(diff)) %>% 
  arrange(desc(maxdiff))
stats <- stats_new
Sys.time()
```




## retrieve ratings

Estimate new ratings in `ratings` project (first), and check that they are up to date


```{r message=FALSE}
england_post=read_ratings("england", 2021)
england_champ_post=read_ratings("england_champ", 2021)
france_post=read_ratings("france", 2021)
germany_post=read_ratings("germany", 2021)
greece_post=read_ratings("greece", 2021)
italy_post=read_ratings("italy", 2021)
scotland_post=read_ratings("scotland", 2021)
spain_post=read_ratings("spain", 2021)
sweden_post=read_ratings("sweden",2020)
europe_post=read_ratings("europe", 2020)
facup_post=read_ratings("facup", 2020)
```


date of last run (more detail in ratings project)

```{r}
last_posterior_date() %>% 
  separate(fname, into=c("league", "ext"), sep="_post") %>% 
  select(-ext) %>% 
  filter(!str_detect(league,"_pre")) %>% 
  arrange(desc(mtime))
```


## leagues --------------------------

### England

```{r england}
newgames("en",stats)
show_teams(england_post$teams)
is_new=0
txt="
8,17,10,Everton v West Brom,4525,2-0:2-1:3-0:3-1:1-0
20,11,10,Leeds v Fulham,4682,2-1:2-0:3-1:1-0:1-1:3-0
3,12,10,Man Utd v Crystal Palace,4740,2-0:2-1:3-1:3-0:1-0:1-1
1,15,10,Arsenal v West Ham,4766,2-0:3-0:3-1:2-1:4-0:1-0
7,9,2,Southampton v Tottenham,4770,1-2:1-1:2-1:0-2:0-1:1-3:2-2:1-0
5,19,0,Newcastle v Brighton,4793,2-1:2-0:1-1:1-0:3-1:2-2
2,4,X,Chelsea v Liverpool,4806,2-2:1-2:1-1:2-1:2-3:1-3:3-2
14,18,10,Leicester v Burnley,4815,2-0:2-1:1-0:3-1:1-1:3-0
6,16,X,Aston Villa v Sheff Utd,4737,1-1:2-1:1-0:1-2:0-1:0-0:2-0:2-2
13,10,21,Wolves v Man City,4738,1-2:1-3:1-1:0-2:2-2:2-1:0-3:2-3
"
d=diff.games(txt,'en',is_new,stats)
d %>% left_join(all_pred(england_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en",stats))
make_new_txt(txt_new, team_tab)
```


### England championship:

```{r england-champ}
newgames("en2",stats)
show_teams(england_champ_post$teams)
is_new=0
txt="
2,16,X,Coventry v QPR,233,1-2:1-1:2-1:0-2:0-1:1-0:2-2:2-0
14,12,0,Nottm Forest v Cardiff,260,2-1:1-1:2-0:1-0:1-2:2-2:3-1:0-1:0-0
5,22,10,Blackburn v Wycombe,264,2-0:2-1:3-0:1-0:3-1:1-1
21,23,10,Brentford v Huddersfield,264,2-0:2-1:1-0:1-1:3-1:3-0:0-1
18,15,X,Luton v Derby,264,1-1:1-2:2-1:1-0:0-2:0-1:2-0:2-2
4,7,X,Middlesbrough v Bournemouth,264,1-2:1-1:2-1:0-2:0-1:1-0:2-2:2-0
1,13,10,Norwich v Preston,264,2-0:2-1:1-0:1-1:3-1:3-0:2-2:1-2
9,19,10,Reading v Barnsley,264,2-0:2-1:1-0:1-1:3-1:1-2:3-0:0-1
8,10,2,Rotherham v Millwall,264,1-1:1-2:0-1:0-2:1-0:2-1:0-0:2-0:2-2
20,6,X,Sheff Wed v Watford,264,1-2:1-1:2-1:0-1:2-2:0-2:1-0:1-3:2-0
24,3,10,Swansea v Birmingham,264,2-1:2-0:1-0:1-1:1-2:0-1
11,17,0,Stoke v Bristol City,273,1-1:2-1:2-0:1-0:1-2:2-2:0-1:0-0:0-2
"
d=diff.games(txt,'en2',is_new,stats)
d %>% left_join(all_pred(england_champ_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("en2",stats))
make_new_txt(txt_new, team_tab)
```

### France

```{r france}
newgames("fr",stats)
show_teams(france_post$teams)
is_new=0
txt="
1,20,10,Lyon v Nîmes,106,2-0:3-0:2-1:1-0:0-0:3-1
12,6,X,Lens v Bordeaux,118,1-1:1-2:2-1:1-3:1-0:0-1:2-0:0-0:0-2
7,2,X,Rennes v Monaco,119,1-1:2-1:1-2:2-2:2-0:0-1:1-0
8,3,21,Nice v PSG,119,1-2:1-3:1-1:0-2:0-1:2-1:0-3:0-4:1-0
18,15,0,Brest v Lorient,120,1-1:2-1:1-0:2-0:0-0:1-2:2-2:3-1
10,17,X,Metz v Reims,119,1-1:0-1:2-1:1-2:1-0:0-0:2-2:2-0:0-2
14,16,10,Montpellier v Angers,119,2-1:1-0:2-0:1-1:0-0
11,19,0,Strasbourg v Dijon,119,1-0:1-1:2-1:2-0:0-0:0-1:1-2:3-1
4,13,X,Nantes v Saint-Étienne,119,1-1:1-2:2-1:1-0:2-0:0-0:0-2:2-2:0-1
5,9,0,Marseille v Lille,119,2-1:1-1:1-0:1-2:2-0:0-0:2-2:3-2:3-1
"
d=diff.games(txt,'fr',is_new,stats)
d %>% left_join(all_pred(france_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("fr",stats))
make_new_txt(txt_new, team_tab)
```


### Germany

```{r germany}
newgames("de",stats)
show_teams(germany_post$teams)
is_new=0
txt="
2,5,10,Bayern Munich v Schalke,151,3-0:3-1:2-0:2-1:4-1:4-0
11,17,10,Frankfurt v DSC Arminia Bielefeld,159,2-0:2-1:3-0:1-0:1-1:3-1:2-2:4-1
12,14,X,Köln v Hoffenheim,159,1-1:1-2:2-1:2-2:1-0:0-1:0-2
15,7,X,Stuttgart v Freiburg,158,1-1:2-1:1-0:1-2:2-0:2-2:0-1:3-1:0-0:0-2
16,13,X,Union Berlin v Augsburg,159,2-1:1-1:2-0:1-0:1-2:0-0:0-1:0-2
1,9,X,Werder Bremen v Hertha Berlin,159,2-1:1-1:1-2:2-2:1-0:3-1:2-0:0-1:0-2
4,8,10,B Dortmund v B Mgladbach,160,2-1:3-1:2-0:1-1:2-2:3-0:3-2
18,10,10,RB Leipzig v Mainz,159,2-0:3-1:3-0:2-1:1-0
6,3,X,Wolfsburg v B Leverkusen,159,1-1:1-2:2-2:2-1:0-2:1-3:1-0
"

d=diff.games(txt,'de',is_new,stats)
d %>% left_join(all_pred(germany_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("de",stats))
make_new_txt(txt_new, team_tab)
```


### Greece

```{r greece}
newgames("gr",stats)
show_teams(greece_post$teams)
is_new=0
txt="
3,9,10,PAOK Salonika v Atromitos Athens,111,2-0:2-1:1-0:3-1:3-0:1-1
2,13,10,Olympiakos v Asteras Tripolis,114,2-0:3-0:2-1:3-1:1-0:4-0:4-1
11,4,2,Panetolikos v AEK Athens,129,0-2:1-2:0-1:1-1:1-3
12,7,X,Lamia v OFI,128,1-1:1-0:1-2:2-1:0-0:2-0:0-1:0-2
14,8,X,Volos NFC v Aris,127,1-1:0-1:1-2:1-0:2-0:2-1:0-0:0-2
"
d=diff.games(txt,'gr',is_new,stats)
d %>% left_join(all_pred(greece_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("gr",stats))
make_new_txt(txt_new, team_tab)
```

### Italy

```{r italy}
newgames("it",stats)
show_teams(italy_post$teams)
is_new=0
txt="
14,15,0,Fiorentina v Torino,139,2-1:1-1:2-0:1-0:3-1:1-2
18,2,21,Hellas Verona v Roma,139,1-2:1-3:0-2:0-1:1-1:0-0
4,16,2,Parma v Napoli,140,1-2:1-1:0-2:0-1:2-1:1-3:2-2
17,10,10,Genoa v Crotone,141,2-0:1-0:2-1:1-1:0-0:3-1
20,13,0,Sassuolo v Cagliari,142,2-1:1-1:1-0:2-0:1-2:2-2:0-0:3-2
3,8,10,Juventus v Sampdoria,140,2-0:3-0:2-1:3-1
1,9,10,AC Milan v Bologna,122,2-0:2-1:3-1:1-0:1-1:3-0
"

d=diff.games(txt,'it',is_new,stats)
d %>% left_join(all_pred(italy_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)

# this needs to be run with d on T
if (is_new) cp_all_pred(italy_post$post,d) %>% select(game,pred) %>% arrange(game)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("it",stats))
make_new_txt(txt_new, team_tab)
```


idea: get predictions from new and old stats, and display only the different ones

### Scotland




```{r scotland}
newgames("sc",stats)
show_teams(scotland_post$teams)
is_new=0
txt="
1,6,10,Celtic v Livingston,278,3-0:4-0:2-0:4-1:3-1:5-0
3,11,0,Dundee Utd v St Mirren,280,2-1:1-0:1-1:2-0:1-2:0-1
7,12,0,Kilmarnock v Hamilton,280,2-1:2-0:1-1:1-0:3-1:1-2
9,10,X,St Johnstone v Ross County,280,1-1:2-1:1-0:2-0:1-2:0-1
5,2,21,Hibernian v Rangers,297,1-2:0-2:1-3:1-1:2-1:2-2:0-1:1-0
8,4,10,Aberdeen v Motherwell,299,2-1:2-0:1-0:3-0:3-1:1-1:2-2
"
d=diff.games(txt,'sc',is_new,stats)
d %>% left_join(all_pred(scotland_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("sc",stats))
make_new_txt(txt_new, team_tab)
```


### Spain

```{r spain}
newgames("es",stats)
show_teams(spain_post$teams)
is_new=0
txt="
8,18,10,Villarreal v Eibar,139,2-0:2-1:1-1:1-0:3-1:3-0
17,7,0,Getafe v Osasuna,154,2-1:1-1:2-0:1-0:1-2:0-1
14,1,X,Celta Vigo v Valencia,142,1-2:1-1:2-1:0-2:1-3:2-2:0-1:1-0
19,10,0,Huesca v Cádiz,153,1-0:1-1:2-1:0-0:0-1:1-2:2-0:2-2
20,16,10,Granada v Alavés,153,2-1:1-0:2-0:1-1:0-1:1-2:0-2
9,12,10,Real Betis v Real Valladolid,152,2-1:2-0:1-0:1-1:1-2:2-2:3-1
11,2,21,Real Sociedad v Real Madrid,152,1-2:1-3:0-2:0-3
"
d=diff.games(txt,'es',is_new,stats)
d %>% left_join(all_pred(spain_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("es",stats))
make_new_txt(txt_new, team_tab)
```



### Sweden

```{r sweden}
newgames("se",stats)
show_teams(sweden_post$teams)
is_new=0
txt="
12,15,X,Falkenbergs FF v Varbergs BoIS,76,1-2:1-1:0-1:2-1:1-0:2-2:2-0
10,9,0,IF Elfsborg v Mjällby AIF,76,2-0:1-1:0-1:2-1:2-2:0-0:1-0:3-1
6,2,X,AIK v Hammarby IF,84,1-1:1-0:1-2:2-1:0-1:0-2:0-0:2-0:2-2:3-0:3-1
16,5,X,Östersunds FK v Djurgårdens IF,84,1-2:1-1:2-1:1-3:0-1:0-2:2-0:0-0
4,3,0,IFK Göteborg v Kalmar FF,85,1-1:2-1:1-0:2-0:0-0:1-2:2-2
11,1,X,IFK Norrköping v Malmö FF,85,2-1:1-1:1-2:1-0:0-0:0-1:1-3:2-2:0-2:2-0
10,13,X,IF Elfsborg v BK Häcken,53,1-0:1-1:2-0:2-1:0-2:1-2:2-2
14,12,0,IK Sirius v Falkenbergs FF,53,2-0:2-1:1-0:1-1:0-0:3-0:3-1
9,8,X,Mjällby AIF v Örebro SK,53,1-1:2-1:0-0:0-1:0-2:1-0:1-2:2-0:2-2
15,7,X,Varbergs BoIS v Helsingborgs IF,53,1-1:1-2:0-0:0-1:1-0:2-1:3-0
"
d=diff.games(txt,'se',is_new,stats)
d %>% left_join(all_pred(sweden_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```



### champions league

```{r}
newgames("euc",stats)
show_teams(europe_post$teams)
is_new=0
txt="
240,138,1,Atalanta v PSG,191,1-2:1-3:2-1:0-2:2-2:1-1:2-3:3-2
653,418,21,RB Leipzig v Atl Madrid,201,1-2:0-1:1-1:0-2:2-1:1-3:1-0:2-2
416,163,1,Barcelona v Bayern Munich,200,1-2:1-3:2-1:2-2:2-3:1-1:0-2
104,136,10,Man City v Lyon,193,3-1:2-1:2-0:3-0:4-1:1-0
653,138,1,RB Leipzig v PSG,168,1-2:1-3:2-1:1-0:1-1:2-2:0-1:0-2
136,163,21,Lyon v Bayern Munich,181,1-3:1-4:1-2:0-2:0-3:0-4:1-1
138,163,1,PSG v Bayern Munich,166,1-2:1-3:2-1:2-3:2-4:2-0:1-1:2-2
"
d=diff.games(txt,'euc',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("euc",stats))
make_new_txt(txt_new, team_tab)
```

### europa league


```{r europa}
newgames("eue",stats)
show_teams(europe_post$teams)
is_new=0
txt="
234,165,10,Inter Milan v B Leverkusen,93,2-1:2-0:1-1:1-0:3-1:1-2
97,84,10,Man Utd v FC Copenhagen,93,2-0:3-1:2-1:3-0:1-0:1-1
467,445,1,Shakhtar Donetsk v FC Basel,108,2-1:2-0:1-2:1-1:1-0:3-1:0-1
106,419,X,Wolves v Sevilla,108,1-2:2-1:1-1:1-0:0-2:1-3:2-2
419,97,X,Sevilla v Man Utd,73,1-2:2-1:1-1:1-0:1-3:2-0:0-0:0-2
234,467,10,Inter Milan v Shakhtar Donetsk,97,2-1:2-0:3-1:3-0:1-0:1-1:1-2:2-2
419,234,1,Sevilla v Inter Milan,94,1-2:1-3:2-1:0-2:1-0:1-1:2-2
"
d=diff.games(txt,'eue',is_new,stats)
d %>% left_join(all_pred(europe_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("eue",stats))
make_new_txt(txt_new, team_tab)
```

### fa cup

```{r facup}
newgames("enf",stats)
show_teams(facup_post$teams)
is_new=0
txt="
18,3,21,Norwich v Man Utd,150,0-2:1-3:1-2:0-3:0-4:0-1:1-1
28,1,X,Sheff Utd v Arsenal,154,1-2:2-1:1-1:1-0:0-1
23,2,X,Leicester v Chelsea,155,1-2:2-1:1-1:1-3:2-2
5,17,21,Newcastle v Man City,157,0-2:1-3:0-3:1-2:2-1
1,17,21,Arsenal v Man City,148,1-2:1-3:0-2:2-1:0-3
3,2,1,Man Utd v Chelsea,157,2-1:1-2:3-1:1-1:2-0:2-2:3-2
1,2,1,Arsenal v Chelsea,92,1-2:2-1:1-3:1-1:2-3:0-2:2-2:0-1
"
d=diff.games(txt,'enf',is_new,stats)
d %>% left_join(all_pred(facup_post$post,d), by="game") %>% 
  select(rowno=row.x, game, pred, rpdiff.y, resnow=resnow.x, res=res.x) %>% 
  filter(is_new | str_detect(rpdiff.y, "[0-9]-[0-9]") | resnow!=res)
```

```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("enf",stats))
make_new_txt(txt_new, team_tab)
```


### junk

league
<chr>
maxdiff
<dbl>
gr	23.529412			
fr	22.500000			
eue	20.388350			
de	18.367347			
sc	16.822430			
en2	16.190476			
es	13.725490			
it	12.244898			
euc	11.147541			
enf	2.061856	


```{r}
team_tab=old_txt_to_numbers(txt)
txt_new=capture.output(newgames("se",stats))
make_new_txt(txt_new, team_tab)
```