## packages

```{r leagues-compare-knit-1}
library(tidyverse)
library(lubridate)
library(rvest)
library(gt)
library(conflicted)
conflict_prefer("filter", "dplyr")
source("20180726_functions.R")
source("stats_functions.R")
```


## get latest preds

```{r leagues-compare-knit-2}
# tmpname <- str_c(tempfile("stats_", "."), ".txt")
# cmd <- str_c("./stats.sh | tee ", tmpname)
# cmd
# system(cmd)
```


log in

```{r leagues-compare-knit-3}
the_url <- "https://www.predictthefootball.com/?lang=en_us"
sess <- session(the_url)
form <- html_form(sess)
# form
filled_form <- html_form_set(form[[1]],
                          "LoginForm[email]" = Sys.getenv("PTF_USER"),
                          "LoginForm[password]" = Sys.getenv("PTF_PASS"),
                          "LoginForm[rememberMe]" = 1
                          )

session_submit(sess, filled_form)
```

get and write to csv

```{r leagues-compare-knit-4}
tmpname <- str_c(tempfile("stats_", "."), ".txt")
tmpname
leagues <- read_csv("short_url.csv")
# leagues %>% mutate(form = map(url, ~get_form(., sess)))
# there is a problem with sweden
# leagues %>% filter(short != "se") -> leagues
# put above back when sweden back
leagues %>% 
  rowwise() %>% 
  mutate(form = list(get_form(url, sess))) -> d
d %>% unnest(form) %>% 
  mutate(fixture = str_c(name_1, " v ", name_2)) %>% 
  select(game = fixture, 
         res = results, 
         league = short,
         howmany = game_number,
         scores
         ) %>% 
  write_csv(tmpname)

```





end of bit I inserted to get rid of perl


## find the two most recent ones

```{r leagues-compare-knit-5}
tibble(files = list.files(pattern = "*.txt")) %>% 
  filter(files != "thing.txt") %>% 
  rowwise() %>% mutate(info = file.mtime(files)) %>% 
  filter(files != "stats.txt") %>% 
  arrange(desc(info)) -> filenames
filenames
```



```{r leagues-compare-knit-6}
stats1 <- read_csv(filenames$files[1])
stats1
stats0 <- read_csv(filenames$files[2])
stats0
```




new games? 

```{r leagues-compare-knit-7}
stats0
stats1
stats1 %>% anti_join(stats0, by="game") -> new_games
new_games
```

ratings (copy for now)

```{r leagues-compare-knit-8}
england_post=read_ratings("england", 2023)
england_champ_post=read_ratings("england_champ", 2023)
france_post=read_ratings("france", 2023)
germany_post=read_ratings("germany", 2023)
greece_post=read_ratings("greece", 2023)
italy_post=read_ratings("italy", 2023)
scotland_post=read_ratings("scotland", 2023)
spain_post=read_ratings("spain", 2023)
sweden_post=read_ratings("sweden",2022)
```

```{r leagues-compare-knit-9}
# france_post$teams %>% View()
```



make correspondence with stats_i and ratings

```{r leagues-compare-knit-10}
league_names <- tribble(
  ~short, ~long,
"de", "germany",
"en", "england",
"en2", "england_champ",
"es", "spain",
"fr", "france",
"gr", "greece",
"it", "italy",
"sc", "scotland",
"se", "sweden"
)
league_names
```

hand edit teams.csv


long is ratings
short is ptf

```{r leagues-compare-knit-11}
teams <- read_csv("teams.csv")
nr <- nrow(teams)
teams %>% mutate(row = gl(nr/2, 2, nr)) %>% 
  pivot_wider(names_from = length, values_from = team) %>% 
  select(-row) -> team_lookup_table
team_lookup_table
```

function to make everything long

```{r leagues-compare-knit-12}
make_long <- function(stats_tab, league_names, team_lookup_table) {
  stats_tab %>% separate(game, into = c("t1", "t2"), sep = " v ") %>% 
  left_join(league_names, by=c("league" = "short")) %>% 
  left_join(team_lookup_table, by=c("t1" = "short")) %>% 
  left_join(team_lookup_table, by=c("t2" = "short")) %>%
  filter(long.x == league.y) %>% 
  select(league, t1 = long.y, t2 = long, res, howmany, scores)
}
```

```{r leagues-compare-knit-13}
new_long <- make_long(new_games, league_names, team_lookup_table)
stats0_long <- make_long(stats0, league_names, team_lookup_table)
stats1_long <- make_long(stats1, league_names, team_lookup_table)
stats1_long
```



function to get posterior predictive dist

```{r leagues-compare-knit-14}
ppd2 <- function(league_name, t1_name, t2_name) {
  ratings <- get(str_c(league_name, "_post"))
  teams <- ratings$teams
  tibble(team = c(t1_name, t2_name)) %>% left_join(teams, by="team") -> ids
  draws <- rstan::extract(ratings$post)
  t1 <- ids$id[1]
  t2 <- ids$id[2]
  tibble(nu1 = draws$o[,t1] - draws$d[,t2] + draws$h,
         nu2 = draws$o[,t2] - draws$d[,t1]) %>% 
    mutate(l1 = exp(nu1), l2 = exp(nu2)) -> d
  nr <- nrow(d)
  d %>% mutate(s1 = rpois(nr, l1), s2 = rpois(nr, l2)) %>% 
    count(s1, s2) %>% 
    mutate(p = n/sum(n)) %>% 
    select(-n) %>% arrange(desc(p))
}
```






```{r leagues-compare-knit-15}
res <- function(s1, s2) {
  case_when(
    s1<s2  ~ "0",
    s1==s2 ~ "1",
    s1>s2  ~ "2" 
    )
}

ptf_pts <- function(p1, p2, o1, o2, resses, scores) {
  pr <- res(p1, p2)
  or <- res(o1, o2)
  r_correct <- pr == or
  s_correct <- (p1 == o1) & (p2 == o2)
  r_bonus <- str_detect(resses, or) & r_correct
  # return(list(pr, or, r_correct, s_correct, r_bonus))
  s_bonus <- !str_detect(scores, str_c(o1, "-", o2)) & s_correct
  r_correct + 2*s_correct + 2*r_bonus + 2*s_bonus
}

ptf_gd <- function(s1, s2) {
  case_when(
    s1 != s2 ~ -abs(s1-s2),
    s1 == 0  ~ 1,
    TRUE     ~ 2*s1
  )
}

cp_pts <- function(p1, p2, o1, o2) {
  pr <- res(p1, p2)
  or <- res(o1, o2)
  pd <- p1-p2
  od <- o1-o2
  diff1 <- abs(p1-o1) + abs(p2-o2) + abs(pd-od)
  diff2 <- abs(p1-o1) + abs(p2-o2)
  case_when(
    pr == or ~ max(20-diff1, 8),
    TRUE     ~ max(8-diff2, 0) 
  )
}
```


expected points by prediction

```{r leagues-compare-knit-16}
ept_ptf <- function(p, resses, scores) {
  crossing(pred1=0:6, pred2=0:6, p) %>% 
    rowwise() %>% 
    mutate(pt = ptf_pts(pred1, pred2, s1, s2, resses, scores)) %>% # goal difference here too
    group_by(pred1, pred2) %>% 
    summarize(ept = sum(pt*p)) %>% 
    arrange(desc(ept)) %>% 
    ungroup() %>% 
    slice(1) %>%
    mutate(pred = str_c(pred1, "-", pred2)) %>% 
    pull(pred)
}

ept_cp <- function(p) {
  crossing(pred1=0:6, pred2=0:6, p) %>% 
    rowwise() %>% 
    mutate(pt = cp_pts(pred1, pred2, s1, s2)) %>% # goal difference here too
    group_by(pred1, pred2) %>% 
    summarize(ept = sum(pt*p)) %>% 
    arrange(desc(ept)) %>% 
    ungroup() %>% 
    slice(1) %>%
    mutate(pred = str_c(pred1, "-", pred2)) %>% 
    pull(pred)
}

```



all the preds

```{r leagues-compare-knit-17}
make_all_preds <- function(long) {
  long %>% 
    filter(league != "england_f") %>% 
    rowwise() %>% 
    mutate(p = list(ppd2(league, t1, t2))) %>% 
    mutate(pred = ept_ptf(p, res, scores)) %>% 
    select(league, t1, t2, pred)
}

make_all_preds_cp <- function(long) {
  long %>% filter(league == "italy") %>% 
    rowwise() %>% 
    mutate(p = list(ppd2(league, t1, t2))) %>% 
    mutate(pred = ept_cp(p)) %>% 
    select(league, t1, t2, pred)
}
```


changes


```{r leagues-compare-knit-18}
Sys.time()
d0 <- read_rds("last_all.rds")
# d0 <- make_all_preds(stats0_long) 
d1 <- make_all_preds(stats1_long)
write_rds(d1, "last_all.rds")
# d0 %>% left_join(d1, by=c("league", "t1", "t2")) %>% 
  # filter(pred.x != pred.y) %>% 
  # mutate(is_same = ifelse(pred.x == pred.y, "same", "** different **")) %>% 
  # filter(league != "england_f") %>% 
  # View("changes")
d1 %>% 
  filter(league != "england_f") %>% gt() # the changes
# View(d1)
```

preds for new, commented out

```{r leagues-compare-knit-19}
#Sys.time()
#make_all_preds(new_long) %>% 
#  filter(league != "england_f") # new games
  # View("new games")
```

italy

```{r leagues-compare-knit-20, error=TRUE}
Sys.time()
make_all_preds_cp(new_long) %>% 
  arrange(t1) %>% 
  gt()
```




## this works.

```{r leagues-compare-knit-21}
# nothing here
```


